\begin{longtable}{|m{3.5cm}|m{10.5cm}|}
    \hline
    
    Certificate Issuance 
    & Authorized administrators can generate academic certificates for eligible students. During issuance, the system:
        \begin{itemize}
            \item Generates a PDF certificate

            \item Calculates a SHA-256 hash of the generated document

            \item Uploads the certificate PDF to IPFS

            \item Creates and uploads a certificate metadata to IPFS

            \item Mints an NFT certificate through the smart contract.

            \item Stores transaction information in MongoDB
        \end{itemize}\\
    \hline

    Certificate Verification 
    & The verification module successfully retrieves certificate information from blockchain records and associated database entries. Users can verify:
        \begin{itemize}
            \item Certificate ownership
            \item Student information
            \item Academic degree details
            \item NFT token identifier
            \item IPFS metadata references
            \item Certificate lifecycle status
        \end{itemize}\\
    \hline

    Tampering Detection
    & To evaluate document integrity protection, modified certificate files were tested against the original blockchain records.

    The SHA-256 hash generated from a modified certificate differed from the hash recorded during issuance. Since the hashes no longer matched, the certificate could not be validated against the stored blockchain information.
    
    This result demonstrates the effectiveness of cryptographic hashing in detecting unauthorized document modifications.\\
    \hline

    AI-Assisted Verification
    & The AI assistant successfully generated natural-language explanations based on verified certificate information supplied by the application. Users were able to ask questions such as:
        \begin{itemize}
            \item Is this certificate authentic?
            
            \item Who owns this NFT certificate?
            
            \item What does the IPFS hash represent?
            
            \item What is the current certificate status?
        \end{itemize}
        
        The assistant translated technical blockchain information into user-friendly explanations, improving accessibility for non-technical users.\\
    \hline

    \caption{Project Results}
    \label{tab:project_result}
\end{longtable}