\subsection{Scope of the Project}

This project focuses entirely on building a blockchain-based platform that uses NFTs to issue and verify school certificates. To keep the project manageable and focused, the scope is strictly limited to the following areas:

\begin{enumerate}

    \item \textbf{Target Users:} The system is built specifically for educational institutions, such as colleges and universities, that need a secure way to hand out academic degrees and professional certificates.

    \item \textbf{Student Benefits:} Graduates and current students receive secure, non-transferable ownership of their achievements through unique NFT-based credentials.

    \item \textbf{Third-Party Verification:} Employers, companies, and external organizations can use the platform's blockchain tools to check the authenticity of any submitted certificate instantly.

    \item \textbf{Core Infrastructure:} We use blockchain technology to keep verification records permanent, alongside Solidity smart contracts to automate how certificates are minted and checked.

    \item \textbf{Data Integrity:} The system relies on SHA-256 cryptographic hashing. This ensures that if anyone alters a document after it is issued, the system catches the modification immediately.

    \item \textbf{Smart Contract Testing:} The scope covers writing, deploying, and testing the actual NFT smart contracts responsible for certificate minting and tracking ownership.

    \item \textbf{Administrative Exclusions:} This platform only handles certificate verification. It deliberately leaves out broader university management features like student enrollment, grading rubrics, tuition tracking, or general school administration systems.

    \item \textbf{Simplified Web Features:} Standard website elements, like public user registration and login pages, are skipped to keep the focus entirely on the NFT authentication logic. Student accounts are generated directly by the system administrator instead.

    \item \textbf{Restricted AI Integration:} We integrated an AI agent into the platform, but its role is strictly limited to helping users read and understand their verification reports. It does not handle any core system logic.

\end{enumerate}